---
title: "Insurance claims prediction"
subtitle: "Coursera reproducible pitch"
author: "Enrique Repullés"
output: slidy_presentation
date: "Jul 26, 2017"
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Introduction

<style type="text/css">
code.r{
  font-size: 15px;
}
pre {
  font-size: 15px
}

</style>

The deployed application makes a prediction of the probability of claims in a car insurance. This can be used to determine the insurance premium.

The application can be viewed at [https://enrique-repulles.shinyapps.io/insurance/]

In the application left panel, the user can introduce the information related to the car insurance and see the prediction on the right panel.

- The source code for the application and this presentation can be found at [https://github.com/enrique-repulles/data-products-shiny]

## Data 

```{r data preparation, echo = FALSE,  message=FALSE}
library(caret)
library(ggplot2)

dataCar<-read.csv("insuranceCarData.csv")
dataCar$agecat <- factor(dataCar$agecat)
dataCar$clm <- factor(dataCar$clm)
dataCar$X<-NULL
dataCar$X_OBSTAT_<-NULL
dataCar$numclaims<-NULL
```
The data set used for the prediction engine has the following structure:

```{r data structure, echo = FALSE,  message=FALSE, }
  summary(dataCar)
```

## Training method

For the machine learning training, the data set was splitted into a training set and a test set (used later to determine accuracy).The algorithm for the training was a basic partitioning tree ("rpart")

```{r training, echo = TRUE,  message=FALSE}
values <- createDataPartition(dataCar$clm, p=.7,list=FALSE)
training <- dataCar[values,]
testing <- dataCar[-values,]
model.fit<-train (clm ~ veh_value + exposure + veh_body +
                  veh_age + gender + area + agecat ,
                  data=training, method="rpart" )

```

## Results
The test data set was used to determine accuracy:
```{r test accuracy, echo = FALSE}
predictions <- predict(model.fit, testing)
confusionMatrix(predictions, testing$clm)
```
Conclusions: The accuracy achieved is not very high, so some time must be invested in find better data.

